---
title: "Triplett Replication"
subtitle: "Sample Analysis on Simulated Data"
author: "*Blinded*"
date: "5th May 2022"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---
  

```{r setup, include=FALSE}
# Setting Up

knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(eval = TRUE, echo = TRUE)
knitr::opts_chunk$set(include = FALSE)
```


```{r}
rm(list = ls())

library(nlme)
library(lme4)
library(ez)
library(simr)
library(rstatix)
library(desnum)

```



# Overview

Below we outline our proposed design along with an accompanying analysis plan. We provide a sample analysis using simulated data.

# Design and Analysis Plan

The proposed study is a within subjects design. The core hypothesis is that the presence of another person completing the same task, will lead to improved performance on that task. Each participant will complete the task four times, twice alone, and twice in the presence of another participant.

## Planned Analysis


### Presence/Competition Effects

To test this we will conduct a mixed effects model with presence included as a fixed effect and participant and presence included as random effects.

```
model1 <- lmerTest::lmer(time ~ 
                           condition
                         + (1+condition|ID), data=x)

summary(model1)
anova(model1)
```

### Order Effects

To test for order effects we blocked our trials by two groups as in the table.


| Trial | Group A     | Group B     |
|:-----:|:-----------:|:-----------:|
| 1     | Alone       | Alone       |
| 2     | Alone       | Together    |
| 3     | Together    | Alone       |
| 4     | Together    | Together    |


A second mixed effect model will include order as a fixed effect, that may interact with condition).

```
model2 <- lmerTest::lmer(time ~ 
                           order*condition
                         + (1+condition|ID), data=x)

anova(model1,model2)
anova(model2)
summary(model2)
```
### Covariates

A third model

```
model3 <- lmerTest::lmer(time ~ 
                           order*condition
                         + age
                         + gender
                         + (1+condition|ID), data=x)

anova(model1, model2, model3)
anova(model3)
summary(model3)
```


### Follow-up Analysis

#### Testing for 'carry-over' presence effects

The above models will provide a test of our hypotheses. However in order to interpret any effects, follow-up analyses will be required.

First we will isolate trials 2 and 3 and conduct a 2x2 mixed between-within ANOVA to test for an interaction between order and presence, across the two groups. The between subjects IV is group (A vs B) and the within subjects IV is condition (together vs alone).

```
rstatix::anova_test(
  data = x, dv = time, wid = ID,
  within = condition,
  between = group
)

#  ---------  #
# for pairwise comparisons

x$condition3 <- paste(x$condition, x$group)

aov1 <- aov(time ~ condition3,x)
summary(aov1)
TukeyHSD(aov1)

```

#### Interpreting Order Effects (between groups)

Because of differences in presence effects, any order effects may vary depending on group/block (A vs B). To test this we will conduct a 2x4 mixed between-within subjects ANOVA with group as the between subjects IV (group A vs group B), and trial number as the within subject IV (4 levels, Trial 1- Trial 4).


```

rstatix::anova_test(
  data = x, dv = time, wid = ID,
  within = order,
  between = group
)

x$condition3 <- paste(x$order, x$group)

aov1 <- aov(time ~ condition3,x)
summary(aov1)
TukeyHSD(aov1)


```

# Power

A-priori power analyses showed that to detect a small effect (*f* ^2^ = .02) a minimum sample of *N* 400 participants is required. Detecting a medium effect (*f* ^2^ = .15) requires a sample of *N* = 54, and detecting a large effect (*f* ^2^ = .35) requires a sample of *N* = 24. We aim to collect 400 participants.

## Small Effect
```{r, include = FALSE}
rm(list = ls())
number_of_participants <- 400
n1 <- 10
n2 <- number_of_participants/2
f <- .02

file.remove("N_power.RData")
```

```{r, include = FALSE}
save(n1,n2,f, file = "N_power.RData")
```

```{r, include = FALSE}
source("power_script.R")
test
pwr::pwr.f2.test(u = test$NumDF, v = test$DenDF, f2 = f, sig.level =  .05)
f_original <- MuMIn::r.squaredGLMM(model1)[1]/(1-MuMIn::r.squaredGLMM(model1)[1])
f_original
pwr::pwr.f2.test(u = test$NumDF, v = test$DenDF, f2 = f, sig.level =  .05)
```

```{r, include = TRUE}
pwr::pwr.f2.test(u = 1, v = 399, f2 = f, sig.level =  .05)
```

## Medium Effect
```{r, include = FALSE}
rm(list = ls())
number_of_participants <- 54
n1 <- 10
n2 <- number_of_participants/2
f <- .15

file.remove("N_power.RData")
```

```{r, include = FALSE}
save(n1,n2,f, file = "N_power.RData")
```

```{r, include = FALSE}
source("power_script.R")
test
pwr::pwr.f2.test(u = test$NumDF, v = test$DenDF, f2 = f, sig.level =  .05)
f_original <- MuMIn::r.squaredGLMM(model1)[1]/(1-MuMIn::r.squaredGLMM(model1)[1])
f_original
pwr::pwr.f2.test(u = test$NumDF, v = test$DenDF, f2 = f, sig.level =  .05)
```

```{r, include = TRUE}
pwr::pwr.f2.test(u = 1, v = 53, f2 = f, sig.level =  .05)
```

## Large Effect
```{r, include = FALSE}
rm(list = ls())
number_of_participants <- 24
n1 <- 10
n2 <- number_of_participants/2
f <- .35

file.remove("N_power.RData")
```

```{r, include = FALSE}
save(n1,n2,f, file = "N_power.RData")
```

```{r, include = FALSE}
source("power_script.R")
test
pwr::pwr.f2.test(u = test$NumDF, v = test$DenDF, f2 = f, sig.level =  .05)
f_original <- MuMIn::r.squaredGLMM(model1)[1]/(1-MuMIn::r.squaredGLMM(model1)[1])
f_original
pwr::pwr.f2.test(u = test$NumDF, v = test$DenDF, f2 = f, sig.level =  .05)
```

```{r, include = TRUE}
pwr::pwr.f2.test(u = 1, v = 23, f2 = f, sig.level =  .05)
```

# Sample Analysis


```{r}

n <- 400 # must be divisible by 2
#n <- 184 # must be divisible by 2
#n <- 184 # must be divisible by 2
N <- 4*n
save(N, file = "N.RData")

source("simulate_data.R")
x <- df

length(x$gender)/4
```


Below we present a sample analysis described above using simulated data for *N* = `r length(x$gender)/4`.

## Hypothesis Testing

### Model 1 Condition

```{r, echo=T}
model1 <- lmerTest::lmer(time ~ 
                           condition
                         + (1+condition|ID), data=x)

summary(model1)
anova(model1)
```


```{r, include=TRUE}
anova(model1)
summary(model1)
```

### Model 2 Condition with Order as Interaction term

```{r, echo=T}
model2 <- lmerTest::lmer(time ~ 
                           order*condition
                         + (1+condition|ID), data=x)


anova(model1,model2)
anova(model2)
summary(model2)

```

```{r, include=TRUE}

anova(model1,model2)
anova(model2)
summary(model2)

```

### Model 3 Covariates Added

```{r, echo=T}
model3 <- lmerTest::lmer(time ~ 
                           order*condition*age
                         + gender
                         + (1+condition|ID), data=x)

anova(model1,model2,model3)
anova(model3)
summary(model3)
```


```{r include=TRUE}
anova(model1,model2,model3)
anova(model3)
summary(model3)
```
 
# Follow-up Analyses

```{r}

x <- df[which(x$order==2|x$order==3),]


```

## Isolate Trials 2 and 3

### Test for 'carry-over' presence effects

#### Basic Descriptive Statistics

```{r, include=TRUE}
tapply(x$time, x$condition, descriptives)
```


```{r, include=TRUE}
tapply(x$time, x$group, descriptives)
```

#### Testing for differences

```{r, include=TRUE}

rstatix::anova_test(
  data = x, dv = time, wid = ID,
  within = condition,
  between = group
)


```

#### Post-hoc Contrast

```{r, include=TRUE}
x$condition3 <- paste(x$condition, x$group)

aov1 <- aov(time ~ condition3,x)
summary(aov1)
TukeyHSD(aov1)


```


```{r, include=TRUE}
tapply(x$time, x$condition3, descriptives)
```

#### Plotting the Responses

```{r, include=TRUE}

ggplot(x,aes(x=(condition3),y=time, fill = condition))+
  geom_violin(width = .4) +
  stat_summary(fun=mean, geom="point", shape=23, size=2, color="black")+
  geom_boxplot(width=0.3, color="black")+
#  geom_dotplot(binaxis='y', stackdir='center', dotsize=.05)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16, position=position_jitter(0.15), size=.3#, color="dark grey"
              )
# violin plot with median points
#p + stat_summary(fun.y=median, geom="point", size=.2, color="red")


```


### Test for Order Effects (depending on group)

#### Basic Descriptive Statistics

```{r}
x <- df
```

```{r, include=TRUE}
tapply(x$time, x$order, descriptives)
```


```{r, include=TRUE}
tapply(x$time, x$group, descriptives)
```

#### Testing for differences

```{r, include=TRUE}

rstatix::anova_test(
  data = x, dv = time, wid = ID,
  within = order,
  between = group
)

```

#### Contrasts

```{r, include=TRUE}
x$condition3 <- paste(x$order, x$group)

aov1 <- aov(time ~ condition3,x)
summary(aov1)
TukeyHSD(aov1)


```


```{r, include=TRUE}
tapply(x$time, x$condition3, descriptives)
```

#### Plotting the Responses

```{r, include=TRUE}

ggplot(x,aes(x=(condition3),y=time, fill = order, color = condition))+
  geom_violin(width = .4) +
  stat_summary(fun=mean, geom="point", shape=23, size=2, color="black")+
  geom_boxplot(width=0.3, color="black")+
#  geom_dotplot(binaxis='y', stackdir='center', dotsize=.05)+
# violin plot with jittered points
# 0.2 : degree of jitter in x direction
  geom_jitter(shape=16, position=position_jitter(0.15), size=.6#, color="dark grey"
              )
# violin plot with median points
#p + stat_summary(fun.y=median, geom="point", size=.2, color="red")


```



